A tutorial of Solving the defined integral problem with OpenMp and Open MPI

### 2023-07-12 documentation/article03/article.tex
Minor fixes

		\subsection{Open MPI}
		\par On line 4 there is a \textbf{required} include for the Open MPI library.
		\begin{lstlisting}[language=C++]
#include <mpi.h>
		\end{lstlisting}

@@

	\section{Conclusion}
		\par The demonstrated example \textbf{does not imply} the superiority of OpenMP over Open MPI because, depending on the problem to be solved and the environment involved, one or the other may be more suitable for the task.

@@

>>>>

		\subsection{Open MPI discussion}
		\par On line 4 there is a \textbf{required} include for the Open MPI library.
		\begin{lstlisting}[language=C++]
#include <mpi.h>
		\end{lstlisting}

@@

	\section{Conclusion}
		\par The demonstrated example \textbf{does not imply} the superiority of OpenMP over Open MPI or the other way around because, depending on the problem to be solved and the environment involved, one or the other may be more suitable for the task.

@@

		\par Hope it helps and, for more information, please consult the references.\newline
